Work Fragmentation in Developer Interaction Data

### 2016-03-19 paper_2.tex
thresholds

>>>>

\paragraph{Discussion of the thresholds}

Interruptions: at least 3 minutes

Prolonged interruptions: at least12 minutes

Num. of interruptions: 
%    -mylyn: none, [1-3], [4-5], [6-10], [>11] (minutes)
%     -udc: none, [1-2], [3-4], [5-7], [>7] (minutes

Proportion of prol. interruptions: 0.50

Recovery time: 15 min, split into 5 minutes phases

Before interruption: 10 minutes before the next interruption

Local analysis: 30 minutes around an interruption

Filtering sessions: at least 30 minutes of duration

Creo que la idea era argumentar (en la respuesta a las revisiones) que explorar otras posibilidades en estos thresholds implica mucho trabajo y experimentos, corrígeme si estoy equivocado.
